---
title: "Plot_hierarchy demo"
author: "Ian Arthur Morelan"
date: "02/25/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
## Quick note
This function only works if your tax table has the following headers: Kingdom, Phylum, Class, Order, Family, Genus.

## Load Packages & Functions
First, if you haven't installed the package, install the hiervis package and load phyloseq. I use the GlobalPatterns dataset for the demo.
```{r setup}

#install.packages(devtools)
#devtools::install_github(fbreitwieser/hiervis)

library(phyloseq)

data("GlobalPatterns")

source("plot_hierarchy.R")



```

## Plot Sankey diagram (default)
It really is as easy as that! This diagram is interactive, so click around to explore the dataset. 

Note: increasing the number of taxa risks overplotting and the function slows down considerably. Interactive Sankey diagrams are better than stacked bar plots, but they still aren't perfect!
```{r message = FALSE}
plot_hierarchy(physeq = GlobalPatterns, number_of_taxa_to_plot = 50)
```

## Plot sunburst
These are essentially Krona plots.
```{r sunburst}
plot_hierarchy(physeq = GlobalPatterns, number_of_taxa_to_plot = 50, plot_type = "sunburst")

```

